Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'GDP, population, and agricultural land growth under the baseline scenario (Source: CEPII and GTM)', digits = 1, escape = FALSE, label = 'baseline-growth')
  ), 1, border_left = TRUE),
  4,
  border_right = TRUE
)

@@

kableExtra::column_spec(
  kableExtra::column_spec(
    kableExtra::kable_styling(
      kableExtra::add_footnote(
        knitr::kable(
          t(out),
          escape = FALSE,
          format = 'latex',
          digits = 1,
          label = 'baseline-forest-change',
          caption = 'Forestland by region in 2023 and estimated change by 2033'
        ),
        label = c(
          'a' = 'Southeast Asia includes Brunei Darussalam, Cambodia, Indonesia, Laos, Malaysia, Myanmar, Philippines, Singapore, Thailand, Timor-Leste, and Vietnam.',
          'b' = 'Oceania includes Australia, Cook Islands, Fiji, French Polynesia, Kiribati, Marshall Islands, Micronesia, Nauru, New Caledonia, New Zealand, Palau, Papua New Guinea, Samoa (Western Samoa), Solomon Islands, Tonga, Tuvalu, and Vanuatu.',
          'c' = 'Rest of South America includes Argentina, Bolivia, Czech Republic, Chile, Colombia, Ecuador, the Falkland Islands, French Guiana, Guyana, Paraguay, Peru, South Georgia, the South Sandwich Islands, Suriname, Uruguay, and Venezuela.',
          d = 'Western & Central Europe includes  Austria, Belgium, Bulgaria, Croatia, Denmark, Estonia, Finland, France, Hungary, Iceland, Italy, Ireland, Germany, Greece, Latvia, Liechtenstein, Lithuania, Luxembourg, Malta, Monaco, Montenegro, Netherlands, North Macedonia, Norway, Poland, Portugal, Romania, Serbia, Slovakia, Slovenia, Spain, Sweden, Switzerland, Turkey, and the United Kingdom.',
          e = 'Other Europe includes Albania, Armenia, Azerbaijan, Belarus, Bosnia and Herzegovina, Georgia,  Kosovo Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, and Ukraine.'
        ),
        threeparttable  = TRUE
      )
    ),
    1,
    border_left = TRUE
  ),
  5,
  border_right = TRUE
)

<!-- Table 1. Forestland by region in 2023 and estimated change by 2033 -->
<!-- 	Russia	Sub-Saharan Africa Brazil Canada Rest of South America	United States Southeast Asia Oceania Western & Central Europe China Central America South Asia Other Europe North Africa & the Middle East Japan East Asia Total  -->
<!-- Forestland in 2023	838.1	564.7	498.2	412.8	348.5	248.4	243.9	199.2	186.7	164.6	94.6	47.8	40.2	33.8	23.7	14.5	3,959.5 -->
<!-- Forestland in 2033	828.7	525.0	479.2	407.9	325.0	249.7	221.3	196.1	175.5	164.8	91.2	42.6	36.1	30.9	26.9	14.6	3,815.3 -->
<!-- $\Delta$ (ha)			-9.5	-39.7	-19.0	-5.0	-23.5	1.3	-22.6	-3.1	-11.1	0.1	-3.4	-5.3	-4.1	-2.9	3.2	0.1	-144.2 -->
<!-- $\Delta$ (%)			-1.1	-7.0	-3.8	-1.2	-6.7	0.5	-9.3	-1.5	-6.0	0.1	-3.6	-11.0	-10.1	-8.5	13.7	0.7	-3.6 -->
<!-- Note: Southeast Asia includes Brunei Darussalam, Cambodia, Indonesia, Laos, Malaysia, Myanmar, Philippines, Singapore, Thailand, Timor-Leste, and Vietnam. Oceania includes Australia, Cook Islands, Fiji, French Polynesia, Kiribati, Marshall Islands, Micronesia, Nauru, New Caledonia, New Zealand, Palau, Papua New Guinea, Samoa (Western Samoa), Solomon Islands, Tonga, Tuvalu, and Vanuatu. Rest of South America includes  -->
<!-- Argentina, Bolivia, Czech Republic, Chile, Colombia, Ecuador, the Falkland Islands, French Guiana, Guyana, Paraguay, Peru, South Georgia, the South Sandwich Islands, Suriname, Uruguay, and Venezuela. Western & Central Europe includes  Austria, Belgium, Bulgaria, Croatia, Denmark, Estonia, Finland, France, Hungary, Iceland, Italy, Ireland, Germany, Greece, Latvia, Liechtenstein, Lithuania, Luxembourg, Malta, Monaco, Montenegro, Netherlands, North Macedonia, Norway, Poland, Portugal, Romania, Serbia, Slovakia, Slovenia, Spain, Sweden, Switzerland, Turkey, and the United Kingdom. Other Europe includes Albania, Armenia, Azerbaijan, Belarus, Bosnia and Herzegovina, Georgia,  Kosovo Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, and Ukraine. 	  -->

@@

<!-- Table 2. Percentage change in the amount of agricultural land in 2033 with deforestation mitigation policy in place (Source: GTAP qo-Land) -->
<!-- 				$\Delta$ (%) -->
<!-- East Asia			-14.6 -->
<!-- Central America			-14.5 -->
<!-- North Africa & the Middle East	-10.3 -->
<!-- Russia				-9.3 -->
<!-- Southeast Asia			-9.0 -->
<!-- Brazil				-8.5 -->
<!-- Rest of South America		-11.7 -->
<!-- South Asia			-8.0 -->
<!-- Canada				-7.9 -->
<!-- West & Central Europe 		-6.2 -->
<!-- Oceania				-5.9 -->
<!-- Sub-Saharan Africa		-4.1 -->
<!-- China				-2.5 -->
<!-- United States			-2.2 -->
<!-- Japan				17.5 -->

@@

Table 3. Percentage change in the amount of agricultural goods produced in 2033 with deforestation mitigation policy in place (Source: GTAP qo-Ag)
				$\Delta$ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

@@

Table 6. Change in market price of various goods in 2033, by region, with deforestation mitigation policy in place (Source: GTAP pm) 
									$\Delta$ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania						1.2	0.4	0.5	0.5	0.5
China						1.1	0.4	0.4	0.4	0.4
Japan						-0.3	0.4	0.4	0.4	0.4
East Asia					5.1	0.3	0.3	0.3	0.4
Southeast Asia					2.8	0.3	0.3	0.4	0.3
South Asia					3.1	0.3	0.3	0.3	0.3
Canada						0.7	0.5	0.5	0.5	0.5
United States					0.7	0.5	0.5	0.5	0.5
Central America					2.5	0.3	0.3	0.4	0.3
Brazil						1.2	0.5	0.5	0.5	0.5
Rest of South America				2.1	0.3	0.3	0.3	0.3
West & Central Europe 				0.9	0.4	0.4	0.4	0.4
Russia						1.1	0.4	0.4	0.4	0.4
Sub-Saharan Africa				1.5	0.4	0.4	0.4	0.4
North Africa & the Middle East			2.0	0.4	0.4	0.4	0.4

Land price seems weird. I have it decreasing????

>>>>

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'GDP, population, and agricultural land growth under the baseline scenario (Source: CEPII and GTM)', digits = 1, escape = FALSE, label = 'baseline-growth')
  ), 1, border_left = TRUE),
  4,
  border_right = TRUE
)
```

@@

kableExtra::column_spec(
  kableExtra::column_spec(
    kableExtra::kable_styling(
      kableExtra::add_footnote(
        knitr::kable(
          t(out),
          escape = FALSE,
          format = 'latex',
          digits = 1,
          label = 'baseline-forest-change',
          caption = 'Forestland by region in 2023 and estimated change by 2033'
        ),
        label = c(
          'a' = 'Southeast Asia includes Brunei Darussalam, Cambodia, Indonesia, Laos, Malaysia, Myanmar, Philippines, Singapore, Thailand, Timor-Leste, and Vietnam.',
          'b' = 'Oceania includes Australia, Cook Islands, Fiji, French Polynesia, Kiribati, Marshall Islands, Micronesia, Nauru, New Caledonia, New Zealand, Palau, Papua New Guinea, Samoa (Western Samoa), Solomon Islands, Tonga, Tuvalu, and Vanuatu.',
          'c' = 'Rest of South America includes Argentina, Bolivia, Czech Republic, Chile, Colombia, Ecuador, the Falkland Islands, French Guiana, Guyana, Paraguay, Peru, South Georgia, the South Sandwich Islands, Suriname, Uruguay, and Venezuela.',
          d = 'Western & Central Europe includes  Austria, Belgium, Bulgaria, Croatia, Denmark, Estonia, Finland, France, Hungary, Iceland, Italy, Ireland, Germany, Greece, Latvia, Liechtenstein, Lithuania, Luxembourg, Malta, Monaco, Montenegro, Netherlands, North Macedonia, Norway, Poland, Portugal, Romania, Serbia, Slovakia, Slovenia, Spain, Sweden, Switzerland, Turkey, and the United Kingdom.',
          e = 'Other Europe includes Albania, Armenia, Azerbaijan, Belarus, Bosnia and Herzegovina, Georgia,  Kosovo Kazakhstan, Kyrgyzstan, Moldova, Tajikistan, and Ukraine.'
        ),
        threeparttable  = TRUE
      )
    ),
    1,
    border_left = TRUE
  ),
  5,
  border_right = TRUE
)
```

@@

@@

@@
